Beyond Adaptive Web Design

### 2014-03-16 paper/paper.tex
fix: motion detected by gyroscope rotation and camera

\subsubsection*{Video Motion} % (fold)
\label{sub:video_motion}

@@

Adaptive input methods provide alternative way of web application control and extend current approach. We have been experimenting to control web applications using voice commands, gyroscope motion and video motion.

@@

We have used device orientation API as alternative control method to web application and built a module which can scroll in website using gyroscope rotation. Developers can use this module as replacement of the global application scroll instead of touch events or mice wheel and also a local element scroll too.

@@

\subsubsection{Video camera motion} % (fold)
\label{ssub:video_camera_motion}

@@

We support 4 direction motion events: swipe from the left to the right, right to left, bottom to top and top to bottom. Using video camera motion we can enhance experience in websites and games. However we need a proper ambient lighting. There can be detection issues in too dark and too bright scenes.

>>>>

\subsubsection*{Video motion detection} % (fold)
\label{sub:video_motion}

@@

Adaptive input methods provide alternative way of web application control and extend current approach. We have been experimenting to control web applications using voice commands, motion detected by a gyroscope or a camera.

@@

We have used device orientation API as alternative control method to web application and built a module which can scroll in website detecting rotation using a gyroscope. Developers can use this module as replacement of the global application scroll instead of touch events or mice wheel and also a local element scroll too.

@@

\subsubsection{Video motion detection} % (fold)
\label{ssub:video_camera_motion}

@@

We support 4 direction motion events: swipe from the left to the right, right to left, bottom to top and top to bottom. Using video motion detection we can enhance experience in websites and games. However we need a proper ambient lighting. There can be detection issues in too dark and too bright scenes.
